---
title: "205_project"
author: "Thong Bui"
date: "11/18/2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Figuring out the correlations from Amazon's overall and NLTK values

This section is using a sample file generated from parse_json.py and find out which variable has the best correlation. Then, 
we will try to combine the variables to figure out the outliers, anomalies to hopefully find out "weird" items

```{r}
library(car)
setwd("~/Desktop/MIDS/205_storage_retrieval/github/w205-project/code/analysis")
sa = read.csv("sample.csv")
summary(sa)
nrow(sa)
scatterplotMatrix(~ overall + neg + neu + pos + compound, data=sa)

(m1=lm(compound ~ overall, data=sa))
plot(sa$overall, sa$compound)
abline(m1)

cor(sa$overall, sa$compound)
cor(sa$overall, sa$pos)
cor(sa$overall, sa$neg)
cor(sa$overall, sa$neu)
```

Because compound values is in the range of (-1, 1) and overall is in the range [0,5], I thought using this function: 

  overall - 5 * compound
  
will help us figure out the outliers


```{r}
plot(sa$overall, -(5*sa$compound) +sa$overall, xlab = "overall", ylab="overall - 5*compound")
```

As you can see, the outliers lay when overall - 5 * compound < -3 or > 8



